### 2018-04-25 article/article.tex

In order to test the TruMan trust model, simulations were made using an implementation of the algorithm in Python.
To generate the input graphs with node mobility, the ONE simulator \cite{keranen2009one} was used in conjunction with the Working Day Movement Model \cite{ekman2008working}, which provides a strong similarity with vehicle movement in real life.
Snapshots of the network were taken every 10 simulated seconds, and these snapshots were used as input for the algorithm.
Malicious nodes misbehave by randomizing the values of their opinions of neighboring nodes.

@@

The concept of trust as applied in VANETs is a powerful tool for those seeking to reduce the spread of false information as much as possible.
In this paper, a new trust model for vehicular networks was presented, which combines the efficiency of previous algorithms in order to generate fast and accurate results.
Nearly all malicious nodes are detected when they constitute up to 50\%, with very few false positives polluting the results, without incurring substantial cost to the vehicles' on-board units.
%The results prove to be accurate, detecting nearly all malicious nodes with very few false positives when they constitute up to 50\% of the network.
%The model is also very efficient thanks to the low complexity of the algorithm constituting the trust model.

>>>>

In order to test the TruMan trust model, simulations were made using an implementation of the algorithm in Python.
To generate the input graphs with node mobility, the ONE simulator \cite{keranen2009one} was used in conjunction with the Working Day Movement Model \cite{ekman2008working}, which provides a strong similarity with vehicle movement in real life.
Snapshots of the network were taken every 10 simulated seconds, and these snapshots were used as input for the algorithm.
Malicious nodes in the simulation misbehave by randomizing their opinions of neighbors (i.e. the trust value of outgoing edges to other nodes).
%The behavior of malicious nodes is to randomize their opinions regarding their neighbors.

@@

The concept of trust as applied in VANETs is a powerful tool for those seeking to reduce the spread of false information as much as possible.
In this paper, a new trust model for vehicular networks was presented, which combines the efficiency of previous algorithms in order to generate fast and accurate results.
Nearly all malicious nodes are detected when they constitute up to 50\% of the network, with very few false positives polluting the results, without incurring substantial cost to the vehicles' on-board units.
%The results prove to be accurate, detecting nearly all malicious nodes with very few false positives when they constitute up to 50\% of the network.
%The model is also very efficient thanks to the low complexity of the algorithm constituting the trust model.

### 2018-04-25 dissertation/4-project/chapter4.tex
dissertation local revision

At first, the node collects and organizes information.
A prerequisite of this step is a test that correctly classifies a neighboring node as benign or malicious.
There are several ways to perform such a test, but a study between these methods is beyond the scope of this paper.
Every time a neighboring node $v$ is tested as benign, the value of $u \rightarrow v$ increases.
Additionally, node $u$ performs an union between its trust graph and $v$'s trust graph, forming a new graph $T^u_i = T^u_{i-1} \bigcup T^v_{i-1}$, which is used for the remaining steps.
Algorithm  \autoref{algorithm:interaction} shows the basic interaction between two nodes, while algorithm \autoref{algorithm:union} details the steps of the graph union.

@@

Furthermore, after each iteration, nodes go through the edges they have stored and discard the ones that are too old.
This is done by setting a maximum age $m$ for edges; once a edge is older than $m$, it is discarded.
A low value for this setting allows for faster detection of converted nodes, however  also increases the likelihood of good information being thrown away (therefore increacing the likelihood of false positive detections).

>>>>

At first, the node collects and organizes information.
A prerequisite of this step is a test that correctly classifies a neighboring node as benign or malicious.
Testing the correctness of neighboring nodes is a problem in and of itself, which is beyond the scope of this project, but studies on this topic can be found on \citep{golle2004detecting}, \citep{kerrache2016detection}, \citep{li2016defective}.

Every time a neighboring node $v$ is tested as benign, the value of $u \rightarrow v$ increases.
Additionally, node $u$ performs an union between its trust graph and $v$'s trust graph, forming a new graph $T^u_i = T^u_{i-1} \bigcup T^v_{i-1}$, which is used for the remaining steps.
Algorithm  \autoref{algorithm:interaction} shows the basic interaction between two nodes, while algorithm \autoref{algorithm:union} details the steps of the graph union.

@@

Furthermore, after each iteration, nodes go through the edges they have stored and discard the ones that are too old.
This is done by setting a maximum age $m$ for edges; once an edge is older than $m$, it is discarded.
A low value for this setting allows for faster detection of converted nodes, however  also increases the likelihood of good information being thrown away (therefore increacing the likelihood of false positive detections).

### 2018-04-25 dissertation/5-simulations/chapter5.tex

>>>>

Malicious nodes in the simulation misbehave by randomizing their opinions of neighbors.
This means that an edge from a malicious node $a$ to another node $b$ is not reliable; its trust value can be anything regardless of the behavior of $b$.
In collusion attacks, malicious nodes intentionally trust other malicious nodes, but such situations were not considered for the evaluation of TruMan.
